Damage localization based on vibrations

### 2017-04-19 rapport/paper.tex
corrected paper

It is of interest to detect damage in infrastructure as quickly as possible whether
 for the potential life-safety or economic impact.
Such detection requires industries to perform some form of SHM.

@@

Traditional methods of damage detection based on visual inspections or experimental techniques such as radiography
 or ultrasound allow to obtain detailed information about a local damage state but requires to know the area where it is located (and hope for easy access).
These techniques may be costly, taking a long time to be performed and impractical to detect damage in large urban areas.
 Furthermore, they may fail if damage is not visibly evident. This is why other global methods automated
 and based on sensor measurements were developed.

@@

Data driven methods are inverse methods that use models based on response data recorded on the structure instead of physical models
\cite{limongelli2016towards}.
Here, a FE model isn't necessary, only recorded data are analyzed.
 In these methods, the damage parameter $D$ is the variation of a damage feature $d$ between the inspection $I$ and the reference $R$ configurations: %Damage-sensitive features are extracted from data and their changes used to identify damage in the structures so the damage parameter D in these method is the variation of the damage feature f between the inspection I and the reference R configurations.
% référence TOWARDS EXTRACTION OF VIBRATION-BASED DAMAGE INDICATORS
% nom pdf : fact sheet template_vibration based_final.pdf

@@

Figure \ref{theo} shows this loss of spatial regularity on the theoretical FRF, for a damage at the position 7.
We can see there is a loss of regularity at the position 7 for the damaged state. We can also see there is an iregularity at the position 2, but here the two states have the same iregularity, so it's not a loss of regularity compared to the reference state.

@@

Then, we calculate for each sensor $z_l$ the cubic polynomial spline interpolation of the transfer functions $H_R(z_k,j)$ measured at all
the other instrumented locations $\{z_k\}, k\in \{1 ... n\}, k \neq l$: we denote it $H_S(z_l,j)$.
The cubic spline interpolation is a piecewise continuous curve, passing through each of the values.
There is a separate cubic polynomial interpolation for each interval, each with its own coefficients.
This is for this local aspect that we use this interpolation (other interpolations can also be used), since we want to detect local iregularities.
Cubic polynomial spline interpolations produce an interpolated function that is continuous through to the second derivative.

@@

Thus, we can have different values of the error interpolation for a same state. The distributions of the erros for a state is close to a gaussian distribution. The problem is that the distributions for an undamaged and a damaged states can be near.

@@

Now, to denote corect detection (or no detection), we will use the terms true positives and negatives, to denote missing alarms we will use false negatives and for false alarms, we will use false positives.

@@

Figure \ref{theodiff} shows the difference betweem the two FRF, and we can see the loss of spatial regularity (damage at position 7).
In comparison with the Figure \ref{theo}, we can see here there is only one iregularity: the fact to compute the difference before the interpolation erase iregularity when they are in the two states. With the initial method, they are also erase when we compute the difference between the interpolation errors.

\begin{figure}[h!]
  \centering
  \includegraphics[width=0.3\textwidth]{images/theodiff60.png}
  \caption{Difference betweem theoretical FRF of undamaged and damage states}
  \label{theodiff}
\end{figure}

Thus, we also study in this paper a variant of the FRF interpolation method . The only difference with the original method is the order of the steps:
\begin{itemize}
\item Compute the FRF
\item Compute the difference between the FRF of reference and the FRF of the studied state, for each frequency
\item Compute the interpolation error of these differencies
\item Compute the sum of the interpolation errors at each frequency
\end{itemize}

@@

Figure \ref{frf_sensors} presents results of the FRF for all the sensors at one frenquency. Curves aren't as regular as the theoretical FRF, but we can see clearly the iregularity between sensors 6 and 7 (there is 10\% of damage here).

@@

With the noise, we can so do two observations: first, the FRF interpolation method has a better localization for small damages than the FRF difference method, second,  the FRF difference method has a better false positives rate than the FRF interpolation method.

@@

Figure \ref{beam_error} shows the computed error. We can see that there are only two sensors with a positiv error, which are the sensors 4 and 5. Thus, the localization is good.

@@

In this paper, we presented the structure health monitoring and a state of the art for this. Then we detailed one of the methods, the FRF interpolation method, and some physical models. Last, we presented our simulation and our results with the implementation of the FRF interpolation method, and analized them.

%nombre de capteurs, fréquences à considérer
We have seen that the FRF interpolation method works, and we proposed a method for eliminate the false positives, and improve its performance. But we have seen that under 10\% of damage, this method doesn't detect damages all the time. To improve the method on that, a study of the considered frequencies could be usefull. Indeed, we have considered all the frequencies under the maximal frequency of the structure here. A selection of the frequencies could permit to detect damages under 10\% extent.

>>>>

Detecting damage in infrastructure as quickly as possible is needed
 for potential life-safety or economic impact.
Such detection requires industries to perform some form of automated SHM.

@@

Traditional methods of damage detection based on visual inspections or experimental techniques such as radiography
 or ultrasound allow to obtain detailed information about a local damage state but requires to know the area where it is located (and the hope of an easy access).
These techniques may be costly, take a long time to be performed and are impractical to detect damage in large urban areas.
 Furthermore, they may fail if damage is not visible because it is not yet critical. This is why other global automated methods
 and based on sensor were developed.

@@

Data driven methods are inverse methods that use models based on response data recorded on the structure instead of physical models
\cite{limongelli2016towards}.
Here, a FE model isn't necessary, only recorded data are analyzed.
 In these methods, the damage parameter $D$ is the variation of a damage $d$ between the inspection $I$ and the reference $R$: %Damage-sensitive features are extracted from data and their changes used to identify damage in the structures so the damage parameter D in these method is the variation of the damage feature f between the inspection I and the reference R configurations.
% référence TOWARDS EXTRACTION OF VIBRATION-BASED DAMAGE INDICATORS
% nom pdf : fact sheet template_vibration based_final.pdf

@@

Figure \ref{theo} shows this loss of spatial regularity on the theoretical FRF, for a damage at the position 7.
We can see there is a loss of regularity at the position 7 for the damaged state. We can also see there is an irregularity at the position 2, but here the two states have the same irregularity, so it's not a loss of regularity compared to the reference state.

@@

Then, we calculate for each sensor $z_l$ the cubic polynomial spline interpolation of the transfer functions $H_R(z_k,j)$ measured at all
the other instrumented locations $\{z_k\}, k\in \{1 ... n\}, k \neq l$: we denote it $H_S(z_l,j)$.
The cubic spline interpolation is a piecewise continuous curve, passing through each of the values.
There is a separate cubic polynomial interpolation for each interval, each with its own coefficients.
This is for this local aspect that we use this interpolation (other interpolations can also be used), since we want to detect local irregularities.
Cubic polynomial spline interpolations produce an interpolated function that is continuous through to the second derivative.

@@

Thus, we can have different values of the error interpolation for a same state. The distributions of the errors for a state is close to a Gaussian distribution. The problem is that the distributions for an undamaged and a damaged states can be near.

@@

Now, to denote correct detection, we will use the terms true positives and negatives, to denote missed alarms we will use false negatives and for false alarms, we will use false positives.

@@

Figure \ref{theodiff} shows the difference between the two FRF, and we can see the loss of spatial regularity (damage at position 7).
In comparison with the Figure \ref{theo}, we can see here there is only one irregularity: the fact to compute the difference before the interpolation erase irregularity when they are in the two states. With the initial method, they are also erase when we compute the difference between the interpolation errors.

\begin{figure}[h!]
  \centering
  \includegraphics[width=0.3\textwidth]{images/theodiff60.png}
  \caption{Difference between theoretical FRF of undamaged and damage states}
  \label{theodiff}
\end{figure}

Thus, we also study in this paper a variant of the FRF interpolation method . The only difference with the original method is the order of the steps:
\begin{itemize}
\item Compute the FRF
\item Compute the difference between the FRF of reference and the FRF of the studied state, for each frequency
\item Compute the interpolation error of these differences
\item Compute the sum of the interpolation errors at each frequency
\end{itemize}

@@

Figure \ref{frf_sensors} presents results of the FRF for all the sensors at one frequency. Curves aren't as regular as the theoretical FRF, but we can see clearly the irregularity between sensors 6 and 7 (there is 10\% of damage here).

@@

With the noise, we can do two observations: first, the FRF interpolation method has a better localization for small damages than the FRF difference method, second,  the FRF difference method has a better false positives rate than the FRF interpolation method.

@@

Figure \ref{beam_error} shows the computed error. We can see that there are only two sensors with a positive error, which are the sensors 4 and 5. Thus, the localization is good.

@@

In this paper, we presented the structure health monitoring and a state of the art for this. Then we detailed one of the methods, the FRF interpolation method, and some physical models. Last, we presented our simulation and our results with the implementation of the FRF interpolation method, and analyzed them.

%nombre de capteurs, fréquences à considérer
We have seen that the FRF interpolation method works, and we proposed a method for eliminate the false positives, and improve its performance. But we have seen that under 10\% of damage, this method doesn't detect damages all the time. To improve the method on that, a study of the considered frequencies could be useful. Indeed, we have considered all the frequencies under the maximal frequency of the structure here. A selection of the frequencies could permit to detect damages under 10\% extent.
